---
title: "ggplot2_coord"
author: "KwH Kim"
date: "2018년 10월 18일"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.height=3)
knitr::opts_chunk$set(fig.width=3)
library(ggplot2)
library(dplyr)
```

## Key components of every plot

1. Data

2. Aesthetic mapping

3. Geoms

4. Auxillary lines

5. **Coordinate System**
    - Coordinate System
        - Cartesian vs. Polar
        - `coord_fixed(ratio = )`, `coord_flip()`, `coord_trans()`
        - `coord_quickmap()`, `coord_map()`
    - Coordinate label
        - `+ labs(x='  ', y='  ')`
    - Breaks & Labels
        - `scale_x_continuous(breaks=c())`
        - `scale_x_continuous(labels=c())` or `scale_x_continuous(labels=NULL)`
    - Zooming
        - Without clipping : `coord_cartesian(xlim = c( , ), ylim = c( , ))`
        - With clipping 
            - `+ xlim( , ) + ylim( , )`
            - `+ scale_x_continuous(limits=c( , ))+scale_y_continuous(limits=c( , ))`
        
        
### Coordinate System

```{r, collapse=T}
d <- ggplot(mpg, aes(fl))
r <- d + geom_bar() 

r + coord_cartesian(xlim = c(0, 5))
r + coord_fixed(ratio = 1/2) 
r + coord_flip()
r + coord_polar(theta = "x", direction=1 ) 
r + coord_trans(y = "sqrt") 
```

### Coordinate label
```{r, collapse=T}
r
r + labs(x='fuel type', y='frequency')
r + labs(x='연료 종류', y='횟수')
```

### Breaks and Labels

```{r, collapse=T}
(n <- d + geom_bar(aes(fill = fl)))
n + scale_fill_manual( 
  values = c("skyblue", "royalblue", "blue", "navy"), 
  limits = c("d", "e", "p", "r"), breaks =c("d", "e", "p", "r"), 
  name = "fuel", labels = c("D", "E", "P", "R"))
n + scale_fill_discrete( 
  #palette = "Blues",
  breaks =c("d", "p"), 
  labels = c("D", "E")) +
  guides(fill='none')
t <- ggplot(mpg, aes(cty, hwy)) + geom_point() 
t + scale_x_continuous(
  breaks=seq(10,40,10), 
  labels=c('ten', 'twenty', 'thirty', 'forty'))
```

### Zooming
```{r, collapse = T}
t <- ggplot(mpg, aes(cty, hwy)) + geom_point() 

# Original
t

# No Clipping
t + coord_cartesian(xlim = c(0, 100), ylim = c(10, 20))

# Clipping 
t + xlim(0, 100) + ylim(10, 20)
t + scale_x_continuous(limits = c(0, 100)) + scale_y_continuous(limits = c(0, 100))
```
