---
title: "ggplot2_title"
author: "KwH Kim"
date: "2018년 10월 18일"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.width=4)
knitr::opts_chunk$set(fig.height=3)
library(ggplot2)
library(dplyr)
```

## Key components of every plot

1. Data

2. Aesthetic mapping
    
3. Geoms
        
4. Auxillary lines

5. Coordinate System & Zooming

6. Legends
    
7. **Title, subtitle, caption and themes**
	- title : `labs(title='  ')`
	- subtitle : `labs(subtitle='  ')`
	- caption : `labs(cpation='  ')`
	- themes 
	    - `+ theme_bw()`
  		- `+ theme_gray()`
  		- `+ theme_dark()`
  		- `+ theme_classic()`
  		- `+ theme_light()`
  		- `+ theme_linedraw()`
  		- `+ theme_minimal()`
  		- `+ theme_void()`
		
## Title, subtitle, and caption

```{r, collapse=T}
t <- ggplot(mpg, aes(cty, hwy, color=cyl)) + geom_point() 
t + labs(title='Fuel economy data')
t + labs(title='Fuel Economy Data',
         subtitle='from 1999 and 2008 for 38 popular models of car')
t + labs(title='Fuel Economy Data',
         subtitle='from 1999 and 2008 for 38 popular models of car',
         caption='Fig. x. This dataset contains a subset of the fuel economy data that the EPA makes available on http://fueleconomy.gov. It contains only models which had a new release every year between 1999 and 2008 - this was used as a proxy for the popularity of the car.')
```

## Themes
```{r, collapse=T}
t <- ggplot(mpg, aes(cty, hwy, color=cyl)) + geom_point() 
t2 <- t + 
  labs(title='Fuel Economy Data',
       subtitle='from 1999 and 2008 for 38 popular models of car',
caption='Fig. x. This dataset contains a subset of the fuel economy data 
that the EPA makes available on http://fueleconomy.gov. 
It contains only models which had a new release every year 
between 1999 and 2008 
- this was used as a proxy for the popularity of the car.')
t2 + theme_bw()
t2 + theme_gray()
t2 + theme_dark()
t2 + theme_classic()
t2 + theme_light()
t2 + theme_linedraw()
t2 + theme_minimal()
t2 + theme_void() 
```

```{r, colllapse=T}
t2 + theme(plot.caption = element_text(hjust = 0))
t2 + theme(plot.caption = element_text(hjust = 0.5))
t2 + theme(plot.caption = element_text(hjust = 1))
t2 + theme(plot.caption = element_text(lineheight=.8, face='bold'))
```

---

### References

* [More about theme](https://ggplot2.tidyverse.org/reference/theme.html)
* [Labels(`+labs()`)](https://ggplot2.tidyverse.org/reference/labs.html)
* [Rotating and spacing axis labels in ggplot2](https://stackoverflow.com/questions/1330989/rotating-and-spacing-axis-labels-in-ggplot2)
* [폰트 설정](https://blog.jongbin.com/2016/12/ggplot2-korean-font/)