---
title: "ggplot2_geoms"
author: "KwH Kim"
date: "2018년 10월 18일"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.height=3)
knitr::opts_chunk$set(fig.width=4)
library(ggplot2)
library(dplyr)
```

## 3 key components of every plot
1. Data
2. Aesthetic mapping(with scale)
3. **Geoms**
    - one instance geoms (ex. `point`, `jitter`, `rug`, `col`, `label`, `text`)
    - summary geoms 
        - 1 variable distribution : `density`, `histogram`, `barplot`
        - 1 variable distribution conditional on another variable : `boxplot`, `violin`
        - 2 variable distribution : `density2d`, `bin2d`, `hex`
        - model : `smooth`, `quantile`

### **Geoms**(mostly from ggplot2 cheatsheet)

#### One Variable - Continous
```{r collapse=T}
c <- ggplot(mpg, aes(hwy)); c2 <- ggplot(mpg)
c + geom_area(stat = "bin")
c + geom_density(kernel = "gaussian")
c + geom_dotplot()
c + geom_freqpoly()
c + geom_histogram(binwidth = 5) 
c2 + geom_qq(aes(sample=hwy))
```

#### One Variable - Discrete
```{r, collapse =  T}
d <- ggplot(mpg, aes(fl))
d + geom_bar() 
```

### Two Variables - x=continous, y=continuous
```{r, collapse = T}
e <- ggplot(mpg, aes(cty, hwy))
e + geom_label(aes(label = cty), nudge_x = 1, nudge_y = 1, check_overlap = TRUE)
e + geom_jitter(height = 2, width = 2) 
e + geom_point()
e + geom_quantile()
e + geom_rug(sides = "bl")
e + geom_smooth(method = lm)
e + geom_text(aes(label = cty), nudge_x = 1, nudge_y = 1, check_overlap = TRUE)
```

```{r}
e + geom_jitter(height=2, width=2, alpha=0.5, size=2) +
  geom_quantile(quantiles=c(0.05, 0.95)) + 
  geom_rug(sides = 'tr') +  # top, bottom, left, right
  geom_smooth(method=lm, size=2) 
# how to remove se of a regression line?
```

```{r}
e + geom_jitter(height=2, width=2, alpha=0.5, size=2) +
  geom_rug(sides = 'tr') +  # top, bottom, left, right
  geom_quantile(method='rqss')
# how to set quantiles to be 0.05, 0.5, 0.95?
# how to change the smoothness?
```

* [More information about `geom_quantile`](https://ggplot2.tidyverse.org/reference/geom_quantile.html)
* [More information about `geom_smooth`](https://stats.idre.ucla.edu/r/faq/how-can-i-explore-different-smooths-in-ggplot2/)

### Two Variables - x=discrete, y=continuous

```{r collapse=T, error=T}
f <- ggplot(mpg, aes(class, hwy))
f + geom_col()
f + geom_bar()
f + geom_boxplot(alpha=0.5)
f + geom_dotplot(binaxis = "y", stackdir = "center")
f + geom_dotplot(binaxis = "y", stackdir = "center", bins=60)
f + geom_violin(scale = "area")
```

```{r collapse=T, error=T}
f <- ggplot(mpg, aes(class, hwy))
f + geom_boxplot(alpha=0.5) + 
  geom_dotplot(binaxis = "y", stackdir = "center", binwidth=1, alpha=0.5)
f + geom_jitter(alpha=0.5, width=0.1, height=0.1) + geom_boxplot(alpha=0.5)
```

### Two Variables - x=discrete, y=discrete

```{r}
g <- ggplot(diamonds, aes(cut, color))
g + geom_count()
g + geom_jitter()
# How to overcome overplot? 1. alpha 2. smaller points
```

### bivariate distribution
```{r, error=F}
h <- ggplot(diamonds, aes(carat, price))
h + geom_bin2d(binwidth = c(0.25, 500)) 
h + geom_density2d()
h + geom_hex()
h + geom_point(alpha=0.2) + 
  stat_ellipse(level=0.95, col="red") + 
  stat_ellipse(level=0.01, col="red", size=3)
```

```{r, error=F}
h2 <- ggplot(diamonds, aes(carat, color))
h2 + geom_bin2d()
h2 + geom_density2d()
h2 + geom_hex() # is this correct?

h3 <- ggplot(diamonds, aes(cut, color))
h3 + geom_bin2d()
h3 + geom_density2d()
h3 + geom_hex() # is this correct?
```

### Maps

```{r}
data <- data.frame(murder = USArrests$Murder,
                   state = tolower(rownames(USArrests)))
map <- map_data("state")
k <- ggplot(data, aes(fill = murder))
k + geom_map(aes(map_id = state), map = map) + expand_limits(x = map$long, y = map$lat)
```
