```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
url0 <- 'https://htmlpreview.github.io/?https://github.com/kwhkim/MJU-2018-02-DataScience/blob/master/00_Instructor/ggplot2/'
htmlFiles <- c(               'ggplot2_aes',
                              'ggplot2_geoms',
                              'ggplot2_lines',
                              'ggplot2_coord',
                              'ggplot2_legend',
                              'ggplot2_title')
htmlUrl <- paste0(url0, htmlFiles, '.html')
i=0
```

# `ggplot2`(gg = **G**rammar of **G**raphics) Summary

## Key components of every plot
1. **Data**
2. [**Aesthetic mapping**](`r i=i+1; htmlUrl[i]`)
    - `mapping` : which aesthetics to use
        - `x`, `y`, `+ facet_grid(y ~ x)` and `+ fact_wrap(~g)`
        - `color`, `fill`
        - `shape`
        - `size`
        - `alpha` : usu. for avoid overplotting
    - `scale` : how to map
        - `x`, `y` : `scale_x_log10()`, `scale_x_reverse()`, `scale_x_sqrt()`
        - discrete `color`, `fill` 
            - `scale_fill_brewer(palette=  )`
            - `scale_fill_grey(start= , end= , na.value= )`
        - continous `color`, `fill`
            - `scale_fill_distiller(palette= )`
            - `scale_fill_gradient(low= , high= )`
            - `scale_fill_gradient(low= , high= , mid= , midpoint= )`
            - `scale_fill_gradientn(colours= )`
        - general 
            - `scale_*_manual(values= )`
            - `scale_*_date(date_labels="%m/%d")`
            - `scale_*_datetime()`
3. [**Geoms**](`r i=i+1; htmlUrl[i]`)
    - one instance geoms (ex. `point`, `jitter`, `rug`, `col`, `label`, `text`)
    - summary geoms 
        - 1 variable distribution : `density`, `histogram`, `barplot`
        - 1 variable distribution conditional on another variable : `boxplot`, `violin`
        - 2 variable distribution : `density2d`, `bin2d`, `hex`
        - model : `smooth`, `quantile`
4. [**Auxillary lines**](`r i=i+1; htmlUrl[i]`)
    - `geom_hline(yintercept= , col= , size= , linetype= )`
    - `geom_vline(xintercept= , col= , size= , linetype= )`
    - `geom_abline(intercept= , col= , slope= )`
    
linetypes
```{r fig.height=1.5, fig.width=6, results=F, echo= F}
lty <- c("solid", "dashed", "dotted", "dotdash", "longdash", "twodash")
linetypes <- data.frame(
  y = seq_along(lty),
  lty = lty
) 
ggplot(linetypes, aes(0, y)) + 
  geom_segment(aes(xend = 5, yend = y, linetype = lty)) + 
  scale_linetype_identity() + 
  geom_text(aes(label = lty), hjust = 0, nudge_y = 0.2) +
  scale_x_continuous(NULL, breaks = NULL) + 
  scale_y_reverse(NULL, breaks = NULL)
```

5. [**Coordinate System**](`r i=i+1; htmlUrl[i]`)
    - Coordinate System
        - Cartesian vs. Polar
        - `coord_fixed(ratio = )`, `coord_flip()`, `coord_trans()`
        - `coord_quickmap()`, `coord_map()`
    - Coordinate label
        - `+ labs(x='  ', y='  ')`
    - Breaks & Labels
        - `scale_x_continuous(breaks=c())`
        - `scale_x_continuous(labels=c())` or `scale_x_continuous(labels=NULL)`
    - Zooming
        - Without clipping : `coord_cartesian(xlim = c( , ), ylim = c( , ))`
        - With clipping 
            - `+ xlim( , ) + ylim( , )`
            - `+ scale_x_continuous(limits=c( , ))+scale_y_continuous(limits=c( , ))`
        
        - `scale_x_continuous(labels=c())` or `scale_x_continuous(labels=NULL)`

		        
6. [**Legends**](`r i=i+1; htmlUrl[i]`)
    - legend title : `+ scale_x_continous(name='  ')`
    - position : `+ theme(legend.position='bottom')`
        - `top`, `left`, `bottom`, `right`
    - legend type : `+ guides(fill='  ')`
        - `none`, `colorbar`, `legend`
    - legend label : `+ scale_x_continuous(labels=c())`
	
7. [**Title, subtitle, caption and themes**](`r i=i+1; htmlUrl[i]`)
	- title : `labs(title='  ')`
	- subtitle : `labs(subtitle='  ')`
	- caption : `labs(cpation='  ')`
	- themes 
	    - `+ theme_bw()`
  		- `+ theme_gray()`
  		- `+ theme_dark()`
  		- `+ theme_class()`
  		- `+ theme_light()`
  		- `+ theme_linedraw()`
  		- `+ theme_minimal()`
  		- `+ theme_void()`
		

### 참고자료 

* RStudio - Help - Cheatsheets - Data Visualization with ggplot2
    
* [R Bookdown](https://bookdown.org/)
    - [Data Visualization](https://socviz.co/)
    - [Fundamentals of Data Visualization](https://serialmentor.com/dataviz/)
    - [R for Data Science](http://r4ds.had.co.nz/)
* [ggplot2-book](https://github.com/hadley/ggplot2-book)
* [Top 50 ggplot2 Visualizations](http://r-statistics.co/Top50-Ggplot2-Visualizations-MasterList-R-Code.html)



