---
title: "ggplot2_aes"
author: "KwH Kim"
date: "2018년 10월 18일"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.height=3)
knitr::opts_chunk$set(fig.width=4)
library(ggplot2)
library(dplyr)
```

## 3 key components of every plot
1. Data
2. **Aesthetic mapping**
    - `mapping` : which aesthetics to use
        - `x`, `y`, `+ facet_grid(y ~ x)` and `+ fact_wrap(~g)`
        - `color`, `fill`
        - `shape`
        - `size`
        - `alpha` : usu. for avoid overplotting
    - `scale` : how to map
        - `x`, `y` : `scale_x_log10()`, `scale_x_reverse()`, `scale_x_sqrt()`
        - discrete `color`, `fill` 
            - `scale_fill_brewer(palette=  )`
            - `scale_fill_grey(start= , end= , na.value= )`
        - continous `color`, `fill`
            - `scale_fill_distiller(palette= )`
            - `scale_fill_gradient(low= , high= )`
            - `scale_fill_gradient(low= , high= , mid= , midpoint= )`
            - `scale_fill_gradientn(colours= )`
        - general 
            - `scale_*_manual(values= )`
            - `scale_*_date(date_labels="%m/%d")`
            - `scale_*_datetime()`
3. Geoms


### Scales

```{r, collapse=T}
d <- ggplot(mpg, aes(fl))
(n <- d + geom_bar(aes(fill = fl)))
n + scale_fill_manual(
  values = c("skyblue", "royalblue", "blue", "navy"),
  limits = c("d", "e", "p", "r"), breaks =c("d", "e", "p", "r"),
  name = "fuel", labels = c("D", "E", "P", "R"))
```

```{r}
mpg$yr = as.Date(as.character(mpg$year), "%Y")
mpg2 <- mpg %>% filter(manufacturer %in% c("audi", "chevrolet", "dodge", "ford"))
ggplot(mpg2, aes(x=yr, y=displ, col=manufacturer)) + 
  geom_jitter() + 
  scale_x_date(date_labels="%Y")
```


```{r}
g <- ggplot(mpg2, aes(x=yr, y=displ, col=manufacturer)) + 
  geom_jitter() 
g + scale_color_manual(values=c('red','blue','gray80','gray70'))
g + scale_color_grey(start=0.2, end=0.8, na.value='red')

g + scale_fill_brewer(palette = "Blues")
```

### Palettes

```{r fig.height=8, fig.width=5}
RColorBrewer::display.brewer.all() 
```

### Scales for x, y

```{r, collapse=T}
g + scale_y_log10()
ggplot(mpg, aes(x=displ, y=hwy)) + geom_point()
p <- ggplot(mpg, aes(x=displ, y=hwy)) + geom_jitter(alpha=0.5)
p 
p + scale_y_log10()
p + scale_x_reverse()
p + scale_x_sqrt()
```

### Facetting

```{r, collpase=T}
t <- ggplot(mpg, aes(cty, hwy)) + geom_point() 
t + facet_grid(. ~ fl)
t + facet_grid(year ~ .)
t + facet_grid(year ~ fl)
t + facet_wrap(~ fl)
```

`scales = ` option
```{r, collapse=T}
t + facet_grid(drv ~ fl, scales = "free")
t + facet_grid(drv ~ fl, scales = "free_x")
t + facet_grid(drv ~ fl, scales = "free_y")
```
 
`labeller = ` option
```{r, collapse=T}
t + facet_grid(. ~ fl, labeller = label_both) 
t + facet_grid(fl ~ ., labeller = label_bquote(alpha ^ .(fl)))
t + facet_grid(. ~ fl, labeller = label_parsed)
```
