```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
url0 <- 'https://htmlpreview.github.io/?https://github.com/kwhkim/MJU-2018-02-DataScience/blob/master/00_Instructor/ggplot2/'
htmlFiles <- c(               'ggplot2_aes',
                              'ggplot2_geoms',
                              'ggplot2_lines',
                              'ggplot2_coord',
                              'ggplot2_legend',
                              'ggplot2_title',
                              'ggplot2_summary')
htmlUrl <- paste0(url0, htmlFiles, '.html')
i=0
```

# ggplot (gg = grammar of graphics)

### 3 key components of every plot
1. **Data**
2. [**Aesthetic mapping**](`r i=i+1; htmlUrl[i]`)
3. [**Geoms**](`r i=i+1; htmlUrl[i]`)
4. [**Auxillary lines**](`r i=i+1; htmlUrl[i]`)
5. [**Coordinate System**](`r i=i+1; htmlUrl[i]`)
6. [**Legends**](`r i=i+1; htmlUrl[i]`)
7. [**Title, subtitle, caption and themes**](`r i=i+1; htmlUrl[i]`)

* [**Summary**](`r i=i+1; htmlUrl[i]`)

We will use `mpg` from package `ggplot2`.[^1]

[^1]: engine displacement=배기량, 
 
Example of basic scatter plots
```{r, eval=F}
ggplot(data, aes(x=  , y=   )) + geom_point()
```

Example of basic scatter plots with more aestheics mappings
```{r, eval=F}
ggplot(data, aes(x=  , y=   , col=  , size=  , shape=   )) + geom_point()
```

Example of basic scatter plot, more geoms
```{r, eval=F}
ggplot(data, aes(x=  , y=   , col=  , size=  , shape=   )) + 
  geom_point() + 
  geom_line()  
```

```{r, eval=F}
ggplot(data, aes(x=  , y=   , col=  , size=  , shape=   )) + 
  geom_point() + 
  geom_line() +
  geom_smooth(method='lm/glm/gam/loess/MASS::rlm', span=  , formula=  )
```

### When x is categorical,
points can be overwritten, so we jitter or convert points to a box or a violin
```{r, eval=F}
ggplot(data, aes(x=  , y=  )) + geom_jitter()
ggplot(data, aes(x=  , y=  , col=  , fill=  )) + geom_boxplot()
ggplot(data, aes(x=  , y=  , col=  , fill=  )) + geom_violin()
```

If y is categorical and x is continuous, you can just flip the plot
```{r, eval=F}
ggplot(data, aes(x=  , y=  )) + coord_flip()
```

### Distribution of a continuous variable: **histograms** and **frequency polygons**
```{r, eval=F}
ggplot(data, aes(x=  )) + geom_historgram(bins=  , binwidth=  , breaks=  )
ggplot(data, aes(x=  )) + geom_freqpoly(bins=  , binwidth=  , breaks=  )  
```

### Distrbution of a categorical variable: **bar chart**
```{r, eval=F}
ggplot(data, aes(x=  )) + geom_bar(col=  , fill= )
```

Examples
```{r, error=T}
ggplot(data, aes(x=  )) + geom_bar()
ggplot(data, aes(x=  )) + geom_bar(aes(col=  ))
ggplot(data, aes(x=  )) + geom_bar(aes(fill=  ))
```

Another bar chart
```{r}
data(mpg, package='ggplot2')
dat <- table(mpg$manufacturer)
df <- as.data.frame(dat)
colnames(df) = c('name', 'n')
ggplot(df, aes(x=name, y=n)) + geom_bar(stat='identity')
```

### 참고자료 

* RStudio - Help - Cheatsheets - Data Visualization with ggplot2
    
* [R Bookdown](https://bookdown.org/)
    - [Data Visualization](https://socviz.co/)
    - [Fundamentals of Data Visualization](https://serialmentor.com/dataviz/)
    - [R for Data Science](http://r4ds.had.co.nz/)
* [ggplot2](https://github.com/hadley/ggplot2-book)
* [Top 50 ggplot2 Visualizations](http://r-statistics.co/Top50-Ggplot2-Visualizations-MasterList-R-Code.html)



